---
title: "Exploring Undergraduate Distance Education in US Schools"
bibliography: testVisual.bib
output: 
  flexdashboard::flex_dashboard:
    theme: united
---

```{r setup, include=FALSE}
library(flexdashboard) # always
```

## Sidebar {.sidebar data-width="375"}

You can find the code for this dashboard at [https://github.com/peregrinechai/Distance_Education](https://github.com/peregrinechai/Distance_Education.git){.uri}

To explore the availability of distance education for undergraduates, I created a custom data set from the Integrated Postsecondary Education Data System. The final data set describes 2,706 institutions which meet the following criteria:

-   Grant undergraduate degrees (associate & bachelor degrees),

-   Located in the United States (within one of the 50 states or District of Columbia), and

-   At least 1 percent of the undergraduate population was enrolled exclusively in distance education during the 2021-22 academic year.

### Key Takeaways

-   For schools at or above the median (**22**) percentage of undergraduates pursuing distance education,

    -   **45%** of these schools are in the public 2-year sector (community colleges).

    -   **66%** of these schools are in the public sector.

-   In-state tuition rates are generally **lower** at schools with high percentages of distance education undergraduates. 

-   4-year schools are more prevalent than 2-year schools for very high rates of distance education undergraduates (75% and above).

-   Tuition rates for in-state undergraduates at 4-year schools are highest in **Vermont** (median of \$42,860) and lowest in **Wyoming** (median of \$3,150).

## Column {.tabset .tabset-fade}

### Distance Education Rates

```{r}
readRDS("del2Draft.rds")
```

### Educational Sectors

```{r}
readRDS("del1Draft.rds")
```

### Tuition Rates Overall

```{r}
readRDS("del3Draft.rds")
```

### In-State Tuition for 4-Year Schools

```{r}
readRDS("del4Draft.rds")
```
